Efficient ancestry and mutation simulation with msprime 1.0

### 2021-08-09 paper.tex
checked my name / affiliation / grant acks
minor fix to UO affiliation
Tree sequence description
This pull request attempted to resolve the following concerns with this paragraph:

Diploid individuals can have *at most* two nodes *at a given locus*. 
Try to avoid using concepts not yet defined (birth time of a lineage, "individual table")
Remove redundancy on defining the node to individual correspondance
Clarify that parent - child nodes may not correspond to parent - child individuals (unless things have changed).

These all mere suggestions.

% Senior Authors
\author[15,$\dagger$]{Simon Gravel}
\author[10,$\dagger$]{Andrew Kern}
\author[23,$\dagger$]{Jere Koskela}
\author[10,24,$\dagger$]{Peter L. Ralph}

@@

% Encoding ancestry
Given a set of sample chromosomes, the topology
of their genetic ancestry is described by a set of \emph{nodes}
and \emph{edges} (Fig.~\ref{fig-ts-example}).
A node in tree sequence terminology corresponds
to a single chromosome strand, associated with its birth time
and other optional information. A node may be
associated with an \emph{individual}, so that, for example, a diploid
individual is associated with two separate nodes (we omit
the individual table in Fig.~\ref{fig-ts-example} as it is optional).
Nodes define haplotypes that exist at a specific time within
some individual, and edges define genetic inheritance
between these nodes. An \emph{edge} consists of a
parent node, a child node and the left and right coordinates
of the contiguous genomic interval over which
the child inherited genetic material from the parent.
Critically, edges can span multiple marginal trees: for
example, in Fig.~\ref{fig-ts-example} the branch from node
0 to 4 is present in both marginal trees, and represented
by a single edge (the first row in the edge table).
This simple device, of explicitly associating tree nodes
with specific ancestral chromosomes and recording the
genomic intervals over which parent/child relationships exist,
generalises the original
``coalescence records'' concept~\citep{kelleher2016efficient},
and is the key to the efficiency of tree
sequences~\citep{
kelleher2018efficient,kelleher2019inferring,ralph2020efficiently}.

>>>>

% Senior Authors
\author[15,$\dagger$]{Simon Gravel}
\author[10,$\dagger$]{Andrew D. Kern}
\author[23,$\dagger$]{Jere Koskela}
\author[10,24,$\dagger$]{Peter L. Ralph}

@@

% Encoding ancestry
Given a set of sample chromosomes, the topology
of their genetic ancestry is described by a set of \emph{nodes}
and \emph{edges} (Fig.~\ref{fig-ts-example}).
A node in tree sequence terminology corresponds to a 
haplotype that existed within a past individual, 
and is ancestral to the sample. 
A diploid individual, for example, is associated with at 
most two separate nodes spanning a given locus. 
The birth time of the individual is recorded as a node 
property. By contrast, recording the identity of the ancestral 
individual is optional because it does not affect sample 
relatedness. Edges define genetic inheritance
between nodes. An \emph{edge} consists of a
parent node, a child node and the left and right coordinates
of the contiguous genomic interval over which
the child node inherited genetic material from the parent node.
Parent and child nodes may correspond to ancestor and descendant 
individuals separated by 
many generations.

Critically, edges can span multiple marginal trees: for
example, in Fig.~\ref{fig-ts-example} the branch from node
0 to 4 is present in both marginal trees, and represented
by a single edge (the first row in the edge table).
This simple device, of explicitly associating tree nodes
with specific ancestral chromosomes and recording the
genomic intervals over which parent/child relationships exist,
generalises the original
``coalescence records'' concept~\citep{kelleher2016efficient},
and is the key to the efficiency of tree
sequences~\citep{
kelleher2018efficient,kelleher2019inferring,ralph2020efficiently}.
